A Large-Scale Study of the Use of Eval in R

### 2020-08-26 inst/paper/main.tex
Add description of miscellaneous eval usage

\newcommand{\eval}{\texttt{eval}\xspace}
\newcommand{\parse}{\texttt{parse}\xspace}
\newcommand{\source}{\texttt{source}\xspace}
\newcommand{\substitute}{\texttt{substitute}\xspace}
\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}
\newcommand{\evil}{\emph{evil}\xspace}
\newcommand{\instrumentr}{\emph{instrumentr}\xspace}
\newcommand{\rdyntrace}{\emph{R-dyntrace}\xspace}
\newcommand{\covr}{\emph{covr}\xspace}
\newcommand{\runr}{\emph{runr}\xspace}

@@

  \subsubsection{Escape Hatch}: \c{eval(unlock_binding ... )} to prevent R CMD check
  warnings

  bypassing R CMD check in the case one accesses dangerous functions such as unlockBinding or private symbols.
 evaling recorded calls in model-fitting functions or passing most of the current call to another function. Both ``patterns'' use the \c{match.call} to capture current call. The latter is just for laziness as it is the same as calling the new function with explicitly selecting the arguments.

>>>>

\newcommand{\eval}{\texttt{eval}\xspace}
\newcommand{\parse}{\texttt{parse}\xspace}
\newcommand{\source}{\texttt{source}\xspace}
\newcommand{\unlockBinding}{\texttt{unlockBinding}\xspace}
\newcommand{\substitute}{\texttt{substitute}\xspace}
\newcommand{\datatable}{\texttt{data.table}\xspace}
\newcommand{\base}{\texttt{base}\xspace}
\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}
\newcommand{\evil}{\emph{evil}\xspace}
\newcommand{\instrumentr}{\emph{instrumentr}\xspace}
\newcommand{\rdyntrace}{\emph{R-dyntrace}\xspace}
\newcommand{\covr}{\emph{covr}\xspace}
\newcommand{\runr}{\emph{runr}\xspace}

@@

  \subsubsection{Convenience}
  evaling recorded calls in model-fitting functions or passing most of the
  current call to another function. Both ``patterns'' use the \c{match.call} to
  capture current call. The latter is just for laziness as it is the same as
  calling the new function with explicitly selecting the arguments.

  \subsubsection{Miscellaneous} \eval is also used in R packages to get around
  various limitations. For example, in \datatable package, \eval is used to modify
  a binding in the \base package of R. Bindings in the \base package are locked
  for modification and require explicit unlocking using \unlockBinding function.
  However using this function directly triggers a warning during package building
  process which statically analyzes the package for use of such restricted
  functions. The \datatable gets around this limitation by enclosing the call to
  \unlockBinding inside \eval.
